Self Regulation Ontology Retest Analyses

### 2018-06-05 code/SRO_Retest_Analyses.Rmd
additional noise ceiling analyses

```{r}
comp_lit_pred_out_task = plyr::rdply(1000, comp_lit_pred(rel_comp %>% filter(task=="task")))
comp_lit_pred_out_task$task = "task"
comp_lit_pred_out_survey = plyr::rdply(1000, comp_lit_pred(rel_comp %>% filter(task=="survey")))
comp_lit_pred_out_survey$task = "survey"
comp_lit_pred_out_both = rbind(comp_lit_pred_out_task, comp_lit_pred_out_task)

What does it look like if you estimate the left one out using the remaining ones for the noise ceiling model?

>>>>

```{r}
comp_lit_pred_out_task = plyr::rdply(1000, comp_lit_pred(rel_comp %>% filter(task=="task")))
comp_lit_pred_out_task$task = "task"
comp_lit_pred_out_survey = plyr::rdply(1000, comp_lit_pred(rel_comp %>% filter(task=="survey")))
comp_lit_pred_out_survey$task = "survey"
comp_lit_pred_out_both = rbind(comp_lit_pred_out_task, comp_lit_pred_out_survey)

comp_lit_pred_out_both %>%
  select(-.n, -m_lit, -m_boot) %>%
  gather(key, value, -task) %>%
  separate(key, c("stat", "sample"), sep = "_") %>%
  ggplot(aes(value, fill=sample, alpha=task, color=task))+
  geom_density(position='identity', size=2)+
  # facet_grid(~task)+
  scale_fill_manual(breaks=c("boot","lit"),
                       labels=c("Empirical", "Literature"),
                      name="Predictor",
                      values = c("purple", "orange"))+
  scale_alpha_manual(breaks=c("survey", "task"),
                     values = c(0.4, 0.7),
                     name="Measure type")+
  scale_color_discrete(name="Measure type")+
  xlab('Variance Explained')+
  ylab('Density')
```

Is this because of less data on surveys? Should I be using a different metric for goodness of fit?

```{r}
table(rel_comp$task)
```

Are the differences in the distributions significant?
The literature does a better job in predicting itself for tasks compared to surveys. s

```{r}
with(comp_lit_pred_out_both, t.test(r2_lit ~ task))
```

Our data is better in predicting the literature for the surveys that it is in predicting tasks.

```{r}
with(comp_lit_pred_out_both, t.test(r2_lit-r2_boot ~ task))
```

What does it look like if you estimate the left one out using the remaining ones for the noise ceiling model?
What is the distance measure?
Sample one row of literature, fit model of sample size+task on remaining data, use that model to predict the reliability estimate plugging in the sample size and task for the sampled row in the model
